\documentclass[10pt]{article}
\usepackage[margin=0.68in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{array}
\usepackage[hidelinks]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.35em}
\setlength{\emergencystretch}{2em}

\newcommand{\revcomment}[1]{\textcolor{black}{\textbf{Reviewer comment. #1}}}
\newcommand{\questionsep}{\par\vspace{1.25em}}
\newcommand{\response}{\textbf{Response.}\enspace}
\newcommand{\needexp}[1]{\textcolor{red}{\textbf{[EXPERIMENT TO INSERT:} #1\textbf{]}}}
\newcommand{\needinfo}[1]{\textcolor{red}{\textbf{[AUTHOR INPUT TO INSERT:} #1\textbf{]}}}

\begin{document}

\begin{center}
{\Large Response to Reviewer kUmZ}\\[2pt]
Submission 13175
\end{center}

\textcolor{red}{Red text marks experimental results or author-supplied facts that must be
inserted and checked before submission.}

\textbf{Opening response.}
We thank the reviewer for focusing on the central validity question: a
cell-centered image does not by itself make the expression target a direct
single-cell measurement. We agree and will sharpen this distinction, broaden the
evaluation, and add the missing construction, cohort, and limitation details.

\questionsep
\textbf{kUmZ-1.}\quad
\revcomment{P2, Q2, L1: the imaging side is cell centered, but spot-level or
interpolated expression does not establish true single-cell prediction. Please
soften the title and abstract.}

\response
We agree. The two platforms must be described separately. Xenium provides
natively cell-resolved transcript locations and platform-defined cell masks. Visium
HD provides dense native 2-\(\mu\)m bin counts that we register to the H\&E image and
aggregate to segmented cell footprints. The latter is a \emph{cell-aligned
computational target}, not direct single-cell ground truth. We will therefore avoid
claims that Visium HD evaluation proves true single-cell expression recovery and
will use ``toward cell-level prediction'' or ``cell-aligned prediction'' where
appropriate. A conservative revised title is:
\emph{sMMC-22M: A Cell-Aligned Multimodal Resource for Spatial Transcriptomics}.

\needinfo{Confirm the final revised title and every title/abstract occurrence of
``single-cell'' that should be retained only for native Xenium measurements.}

For lung A, lung B, and ovary, strict-interior assignment retained
\(62.5\%/56.1\%/80.7\%\) of default cells and
\(16.0\%/11.0\%/20.5\%\) of assigned bins. One-bin erosion retained
\(46.0\%/37.9\%/72.0\%\) of cells, whereas dilation retained essentially all cells
but increased assigned bins to \(181.9\%--196.2\%\) of default. This material
sensitivity reinforces the revised cell-aligned, rather than direct single-cell,
claim.

\needexp{Insert matched-cell expression/marker/state agreement and fixed-checkpoint
downstream sensitivity with confidence intervals for these completed perturbations.}

\questionsep
\textbf{kUmZ-2.}\quad
\revcomment{P3 and Q1: the experiments emphasize only a few organs. If all 25 organs
were evaluated, report per-organ and summary performance.}

\response
We did not train and validate the same complete benchmark on all 25 organs, and we
will not imply that we did. We can currently add an audited, directly comparable
five-organ Visium HD result:

\begin{center}
\begin{tabular}{lrrrr}
\toprule
Organ & Gene \(r\) & Gene \(\rho\) & Cell \(r\) & Cell \(\rho\) \\
\midrule
Ovary  & 0.4523 & 0.4813 & 0.8379 & 0.7785 \\
Lung   & 0.5178 & 0.5077 & 0.6042 & 0.5452 \\
Breast & 0.3366 & 0.2631 & 0.2345 & 0.2393 \\
Kidney & 0.3643 & 0.3313 & 0.5112 & 0.4834 \\
Tonsil & 0.3817 & 0.3354 & 0.8193 & 0.5670 \\
\bottomrule
\end{tabular}
\end{center}

This is an in-domain top-50-gene diagnostic and will be labeled as such. Its wide
range also argues against reporting only a pooled score.

Separately, native-Xenium in-domain diagnostics give gene Pearson/Spearman of
\(0.541/0.544\) (colon; 77,636 cells), \(0.512/0.585\) (breast; 114,907),
\(0.406/0.459\) (ovary; 4,000), and \(0.509/0.384\) (skin; 13,696), with
interpretable TFF3/EPCAM, MUC1/GATA3, and DES/MYH11/MYLK signals. These
training-selected, random-cell panels support native-target feasibility, not
sample-held-out generalization.
Their image-model/coordinate-only gene-wise Pearson values were
\(0.541/0.238\), \(0.512/0.116\), \(0.406/0.285\), and \(0.509/0.257\);
100-replicate spatial-block bootstrap intervals did not overlap for any sample.

\needexp{Insert the lightweight per-organ/platform and native-Xenium
sample-held-out summaries, separated by platform, with baselines and uncertainty.}

\questionsep
\textbf{kUmZ-3.}\quad
\revcomment{P4: the ovarian age experiment demonstrates distribution shift but does
not advance the single-cell claim.}

\response
We agree. We will present this experiment only as a metadata-defined distribution
shift case study. It does not validate cell-level target accuracy or establish a
causal age effect. AK, AD, and AL are anonymized ovarian sample IDs; the current
comparisons also differ in patient/tumour context and gene-panel size.

\needexp{Rerun the ovarian comparisons on one shared gene panel with matched
preprocessing and report cell/sample counts and uncertainty. State only an
age-associated observation, with patient/tissue-state confounding, if it remains
supported.}

\questionsep
\textbf{kUmZ-4.}\quad
\revcomment{P5--P7: the manuscript repeats its framing but omits alignment details;
STBoost is defined too late, and Figure 1 contains errors.}

\response
We will use the saved space to move concrete details into the main text. The
construction section will state how cells are obtained for each platform, how
coordinates are registered, how Visium HD bins are assigned to footprints, and how
QC is applied. STBoost will be introduced in the abstract and introduction as a
data-interface framework. STBoost-Ref will be defined as the image-only
retrieval-based predictor before its first result. At inference it receives local
and wider-context histology crops and outputs a cell-aligned expression vector;
query expression is not an input.

The audited released rule uses closed native 2-\(\mu\)m bin squares intersecting
CellViT polygons. Multi-cell claims are resolved by nearest CellViT centroid in
full-resolution coordinates, with lower raw-cell index as an exact-tie breaker.

\needinfo{Insert the CellViT and registration implementation versions,
cell--bin center-distance summary, QC thresholds, and the fraction of cells/bins
retained per platform.}

We will redraw Figure 1, correct ``Hierarchical'' and ``Resolution (Single \ldots),''
complete the LLM-agent labels, expand the caption, remove the partial Figure 3
border, and render figure text as text rather than raster. Table 1 will define
``study split'' and point to the split appendix. Table 2 will define a ``cell unit''
as one aligned cell record and point to the construction section. Figure 2 and its
caption will define the training-data ratio. We will also make the suggested cuts
around lines 107 and 115 and clearly state the public release scope in place of the
ambiguous sentence around line 268.

\questionsep
\textbf{kUmZ-5.}\quad
\revcomment{P8: report patient/animal counts and the numbers used in cross-patient
training and testing.}

\response
We agree that cell counts alone can exaggerate biological sample size.

\needinfo{Insert total and per-organ counts of human patients, animal subjects,
studies, specimens, and sections; for every transfer experiment, insert the
train/validation/test patient or animal IDs and their cell counts. State how repeated
sections from one subject are grouped to prevent leakage.}

\questionsep
\textbf{kUmZ-6.}\quad
\revcomment{P9: audit sex, ethnicity, and other traits that may be imbalanced or
missing.}

\response
We agree and will add a coverage and missingness audit using only metadata reported
by the source studies. We will not infer ethnicity or other sensitive attributes
from images or names. Missingness will be reported as a limitation, and performance
will be stratified only where group size and consent permit responsible reporting.

\needexp{Insert the demographic/biological-context coverage table by platform and
organ (sex, age, ethnicity where reported, disease state, and missingness), together
with subgroup sample sizes and any sufficiently powered stratified performance
analysis.}

\questionsep
\textbf{kUmZ-7.}\quad
\revcomment{Q3: compare cell-aligned performance with spot-centered performance.}

\response
This is a useful requested control. A valid comparison must use the same tissue
region, genes, train/test split, encoder, and metric; cell predictions should be
re-aggregated to spots so both methods are evaluated against the same measured
spot-level target. This tests whether cell alignment preserves or improves
spot-level consistency, but it still cannot by itself prove within-spot single-cell
accuracy.

\needexp{Insert the matched spot-versus-cell experiment: spot-centered baseline,
cell-aligned model re-aggregated to the same spots, identical genes/splits, spatial
buffer control, per-gene and per-spot metrics, and uncertainty.}

\questionsep
\textbf{kUmZ-8.}\quad
\revcomment{Q4: explain how spot/bin expression is matched to cells and consider
renaming sMMC-22M to reflect the current count.}

\response
The main text will describe the full matching algorithm before the experiments and
will use ``bin-to-cell aggregation'' rather than ``interpolation'' unless an
interpolation step is actually performed. The audit resolves the previous count
ambiguity. The public-data inventory contains 23,943,826 mixed upstream/source
units (16,314,129 Xenium native cells plus 7,629,697 Visium HD pre-aggregation
records), whereas its native-plus-derived expression matrices contain 20,246,169
aligned target rows because the 2-\(\mu\)m bin-to-cell matrices contain 3,932,040
derived rows. Four in-house Yale pilot DBiC-seq cell-line samples add 9,806
measured and aligned cells. The corresponding record-level totals are therefore
23,953,632
measured/source units and 20,255,975 aligned target cells, across 70 unique source
samples represented by 71 processing records. We will report both counting layers
explicitly and use one consistently for the release headline.

\needinfo{Choose one naming policy before submission: retain ``sMMC-22M'' as a
versioned brand and explain it once, or rename consistently throughout the paper,
repository, figures, and release files.}

\questionsep
\textbf{kUmZ-9.}\quad
\revcomment{L2--L4: the limitations are vague about transfer tests, errors exposed
by cell alignment, and alignment/metadata coverage.}

\response
We will replace the current limitations paragraph with explicit statements:
(i) within-sample results may reflect spatial interpolation and do not establish
patient-level generalization; (ii) sample-held-out tests expose, but do not solve,
biological and acquisition shifts; (iii) native Xenium and derived Visium HD targets
have different evidentiary status; (iv) segmentation and boundary assignment can
propagate errors to cell-aligned profiles; (v) metadata and demographic coverage are
uneven and sometimes absent; and (vi) histology-to-expression predictions must not
be treated as substitutes for molecular measurement.

\needexp{Insert a distance-buffered split and spatial-only baseline to quantify the
extent of within-sample spatial autocorrelation.}

\end{document}
