\documentclass[10pt]{article}
\usepackage[margin=0.72in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{array}
\usepackage[hidelinks]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.45em}
\setlength{\emergencystretch}{2em}

\newcommand{\revcomment}[1]{\textcolor{black}{\textbf{Reviewer comment. #1}}}
\newcommand{\questionsep}{\par\vspace{1.25em}}
\newcommand{\response}{\textbf{Response.}\enspace}
\newcommand{\needexp}[1]{\textcolor{red}{\textbf{[EXPERIMENT TO INSERT:} #1\textbf{]}}}
\newcommand{\needinfo}[1]{\textcolor{red}{\textbf{[AUTHOR INPUT TO INSERT:} #1\textbf{]}}}

\begin{document}

\begin{center}
{\Large Response to Reviewer aSvP}\\[2pt]
Submission 13175
\end{center}

\textcolor{red}{Red text marks experimental results or author-supplied facts that must be
inserted and checked before submission.}

\textbf{Opening response.}
We thank the reviewer for recognizing the value of a cell-aligned spatial
transcriptomics resource at this scale. We agree that scale alone is not sufficient:
the resource should expose concrete analysis challenges and enable conclusions that
smaller, less diverse collections cannot support. We will therefore make the
benchmark objectives and the effects of dataset heterogeneity more explicit.

\questionsep
\textbf{aSvP-1.}\quad
\revcomment{The extent to which the larger, higher-resolution, and context-rich
dataset can promote research progress is not fully explained.}

\response
The intended contribution is not a claim that one predictor solves
histology-to-expression inference. Rather, sMMC-22M makes three previously difficult
evaluations practical:

\begin{enumerate}
  \item \textbf{Breadth and transfer:} models can be evaluated by organ, platform,
  study, and patient instead of only by a pooled random split.
  \item \textbf{Cell-aligned resolution:} each record links a cell-centered local
  image, a wider tissue-context image, coordinates, and an expression target. For
  Xenium the molecular measurements are natively cell resolved; for Visium HD the
  target is a boundary-aware aggregation of native 2-\(\mu\)m bins and will be described as
  \emph{cell-aligned}, not as error-free single-cell ground truth.
  \item \textbf{Context-aware failure analysis:} metadata allow performance to be
  stratified rather than hiding patient, organ, or acquisition shifts in a pooled
  score.
\end{enumerate}

As an initial breadth check, we evaluated the same image-only reference predictor
(STBoost-Ref) on five Visium HD organs using a common in-domain top-50-gene
diagnostic. Gene-wise Pearson correlation ranges from \(0.3366\) to \(0.5178\), while
cell-wise Pearson correlation ranges from \(0.2345\) to \(0.8379\):

\begin{center}
\begin{tabular}{lrrrr}
\toprule
Organ & Gene \(r\) & Gene \(\rho\) & Cell \(r\) & Cell \(\rho\) \\
\midrule
Ovary  & 0.4523 & 0.4813 & 0.8379 & 0.7785 \\
Lung   & 0.5178 & 0.5077 & 0.6042 & 0.5452 \\
Breast & 0.3366 & 0.2631 & 0.2345 & 0.2393 \\
Kidney & 0.3643 & 0.3313 & 0.5112 & 0.4834 \\
Tonsil & 0.3817 & 0.3354 & 0.8193 & 0.5670 \\
\bottomrule
\end{tabular}
\end{center}

These results should be read as a diagnostic of cross-tissue difficulty, not as a
claim of uniformly accurate molecular prediction. They show why a multi-organ
resource matters: a pooled mean would conceal very different gene- and cell-level
behavior. We will add this compact summary and label the gene selection protocol
explicitly. In a separate lung analysis of 111,772 cells, marker-derived coarse
cell-state prediction from inferred expression reaches \(0.5935\) accuracy and
\(0.5922\) balanced accuracy (ARI \(0.1362\), NMI \(0.2154\)). The moderate
agreement is useful calibration: predicted expression retains some biological
signal, but is not a substitute for direct molecular measurement.

We additionally audited four existing evaluations whose expression targets are
native Xenium segmented cells. Under a fixed 70/10/20 within-sample random-cell
split and training-selected top/HVG panels, colon (\(n=77{,}636\) test cells) and
breast (\(n=114{,}907\)) achieved gene-wise Pearson/Spearman correlations of
\(0.541/0.544\) and \(0.512/0.585\), respectively. Ovary
(\(n=4{,}000\)) and skin (\(n=13{,}696\)) yielded
\(0.406/0.459\) and \(0.509/0.384\). Recovered genes included
TFF3/EPCAM and IGKC/JCHAIN in colon, MUC1/GATA3 in breast, and a coherent
DES/MYH11/MYLK/ACTG2/ACTA2 smooth-muscle program in skin. These results provide
marker-level evidence on native targets, but the random-cell split may exploit
within-sample spatial structure and is not evidence of sample-held-out
generalization.

Against coordinate-only baselines, image-model gene-wise Pearson correlation was
\(0.541\) versus \(0.238\) in colon, \(0.512\) versus \(0.116\) in breast,
\(0.406\) versus \(0.285\) in ovary, and \(0.509\) versus \(0.257\) in skin.
Across 100 spatial-block bootstrap replicates, none of the four image-model
gene-correlation 95\% confidence intervals overlapped its coordinate-only interval.

\needexp{Insert the ongoing native-Xenium sample-held-out benchmark with
training-mean, coordinate-only, and metadata-only baselines; report prespecified
marker/program and coarse-state metrics, per-sample values, and uncertainty.}

\questionsep
\textbf{aSvP-2.}\quad
\revcomment{The increased scale, resolution, and context may also increase
heterogeneity. Please clarify that heterogeneity and how it influences downstream
analysis.}

\response
We agree. Our canonical audit separates source-package counts from final expression
targets. The public component contains 42 native Xenium packages with 16,314,129
target cells and 25 Visium HD source packages with 7,629,697 pre-aggregation
source/segmentation records. The canonical 2-\(\mu\)m bin-to-cell matrices contain
3,932,040 derived Visium HD target rows, giving 20,246,169 public aligned targets
across 25 species--organ strata. Four in-house Yale pilot DBiC-seq cell-line
samples add 9,806 measured and aligned cells, for a record-level total of
20,255,975 aligned
targets. The release therefore contains 70 unique source samples represented by 71
processing records; these records are not independently verified studies or
donors.

Among the public tissue strata, the imbalance is substantial: target counts range
from 26,366 (human heart) to
3,559,793 (human breast), a 135-fold range; the median is 384,121
(IQR 225,906--880,627). Gene coverage ranges from 450 to 72,302, and only 10 of
25 strata are represented on both platforms. Organs also differ in tissue state,
morphology, donor composition, and metadata completeness.
Consequently, randomly pooled performance can be dominated by the largest
organ/platform strata and can overstate generalization through spatial or
within-sample autocorrelation.

We will make these consequences operational in the benchmark:

\begin{itemize}
  \item report platform-separated and organ-macro averages rather than only a
  cell-weighted pooled average;
  \item publish split keys at the highest verified biological unit and distinguish
  in-domain interpolation from cross-sample transfer; ``cross-patient'' will be used
  only where independent patient IDs are documented;
  \item report gene-panel overlap and metadata missingness for each evaluation;
  \item attach a provenance label to every field (directly measured, processed, or
  generated), so users can select a reliability tier appropriate to their task.
\end{itemize}

\needinfo{Complete the audited heterogeneity table with evidence-backed biological
sample and donor/patient IDs, tissue-state labels, and metadata missingness. The
organ/platform cell counts, gene ranges, and long-tail statistics are already
verified; donor-level claims remain unsupported until these fields are supplied.}

\needexp{Insert stratified downstream results showing how performance changes across
platforms, organs, patients/studies, panel-overlap bins, and metadata-completeness
bins. Report macro averages and variability; do not pool all cells into one score.}

We will also revise the limitations to state directly that sMMC-22M reflects the
composition of its contributing studies, that uncommon organs and demographic
groups may be underrepresented, and that processed Visium HD cell profiles inherit
segmentation and aggregation uncertainty. These changes turn heterogeneity from an
unreported nuisance into an explicit benchmark variable and a documented limitation.

\questionsep
\textbf{Planned manuscript changes.}
We will (i) add the platform/organ composition and heterogeneity tables, (ii) add the
five-organ result summary and the broader biological evaluation once completed,
(iii) define all split levels and macro-averaging rules, and (iv) expand the
limitations and field-level provenance documentation.

\end{document}
