\documentclass[10pt]{article}
\usepackage[margin=0.70in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{array}
\usepackage[hidelinks]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.38em}
\setlength{\emergencystretch}{2em}

\newcommand{\revcomment}[1]{\textbf{Reviewer comment.} \emph{#1}}
\newcommand{\response}{\textbf{Response.}}
\newcommand{\needexp}[1]{\textcolor{red}{\textbf{[EXPERIMENT TO INSERT:} #1\textbf{]}}}
\newcommand{\needinfo}[1]{\textcolor{red}{\textbf{[AUTHOR INPUT TO INSERT:} #1\textbf{]}}}

\begin{document}

\begin{center}
{\Large Response to Reviewer 7Gar}\\[2pt]
Submission 13175
\end{center}

\textcolor{red}{Red text marks experimental results or author-supplied facts that must be
inserted and checked before submission.}

\textbf{Opening response.}
We thank the reviewer for identifying places where our framing ran ahead of the
evidence. We agree that a useful benchmark must state the scientific question,
evaluation unit, inputs, targets, metrics, and conclusion for each experiment. We
will substantially reorganize the paper around these items and narrow claims where
the target is computationally derived.

\medskip
\textbf{7Gar-1.}\quad
\revcomment{The purpose and biological meaning of the scale, resolution, and context
experiments are unclear.}

\response
We will replace the repeated three-axis narrative with the following explicit
benchmark map:

\begin{center}
\begin{tabular}{p{0.12\linewidth}p{0.24\linewidth}p{0.30\linewidth}p{0.24\linewidth}}
\toprule
Axis & Question & Design & Intended conclusion \\
\midrule
Scale &
Does broader training coverage improve image-to-expression prediction and encoder
comparison? &
Image-only prediction under fixed genes, splits, and metrics while varying training
coverage. &
Whether additional coverage helps, and where organ/platform heterogeneity limits
transfer. \\
Resolution &
Does a cell-aligned interface expose within-region variation hidden by spot
averaging? &
Compare baselines and STBoost-Ref on cell-aligned targets, separately for native
Xenium and processed Visium HD. &
Benchmark feasibility and uncertainty, not proof of true single-cell recovery from
histology. \\
Context &
Can metadata-defined shifts reveal failures hidden by pooled testing? &
Patient/study/context-held-out evaluation with matched preprocessing and gene panel. &
Characterize a specific distribution shift; do not infer a causal biological effect. \\
\bottomrule
\end{tabular}
\end{center}

Figure 2 evaluates histology-image-to-gene-expression prediction. Gene-wise Pearson
and Spearman correlations measure per-gene agreement across cells; cell-wise
correlations measure profile agreement within cells. The horizontal ratio is the
fraction of the available training reference set used.

\needexp{Insert the audited Figure 2 scale results for every plotted ratio, with the
exact number of training cells, test samples, repetitions/seeds, confidence
intervals, and a statement of whether the curve supports a scaling trend. Do not
reuse the unverified encoder/ratio table from the method manuscript.}

For resolution/breadth, an audited five-organ Visium HD diagnostic yields
STBoost-Ref gene-wise Pearson correlations of \(0.4523\), \(0.5178\), \(0.3366\),
\(0.3643\), and \(0.3817\) for ovary, lung, breast, kidney, and tonsil,
respectively. We will add the complete per-organ table and emphasize the substantial
variation rather than only a pooled average.

For context, we agree that the ovarian analysis is currently a case study. AK, AD,
and AL are anonymized ovarian sample identifiers; the comparison also changes
patient/tissue context and currently uses unequal gene panels. Therefore it does not
isolate an age effect.

\needexp{Rerun AK--AD and AK--AL using the identical shared gene panel, preprocessing,
metrics, and uncertainty estimates; insert the result and rewrite the claim as
``age-associated'' only if supported while explicitly retaining patient/tissue-state
confounding.}

\medskip
\textbf{7Gar-2.}\quad
\revcomment{The cell-level profiles and generated textual context are derived but
not validated; the pipeline and example records should be shown.}

\response
We agree. We will distinguish platform-native measurements from derived fields.
Xenium provides transcript coordinates and cell masks. For Visium HD, registered
8-\(\mu\)m bin counts are aggregated to segmented H\&E cell footprints; these are
cell-aligned computational targets, not direct single-cell measurements. Textual
captions are metadata-grounded generated annotations and are not used as molecular
ground truth. A representative record will show the raw provenance, local and
context crops, coordinates, processed expression, metadata, generated text, and
split key.

\needinfo{Insert the exact boundary-bin assignment rule, segmentation model/version,
registration procedure, QC thresholds, and the number/fraction of cells and bins
removed by each QC step.}

\needexp{Insert Visium HD validation under boundary-bin discard and mask
erosion/dilation, with retained-cell rates, expression agreement, marker consistency,
and downstream sensitivity; include cell-resolved external concordance where
available.}

\needexp{Insert a blinded human factuality audit of generated captions: number of
records and raters, expertise, rubric, supported/unsupported statement rates, error
types, and inter-rater agreement. Until then, label captions as optional unvalidated
generated fields.}

\medskip
\textbf{7Gar-3.}\quad
\revcomment{Please quantify the genuinely new in-house contribution relative to
aggregated public resources such as HEST-1K and STimage-1K4M.}

\response
We agree that our current wording is ambiguous. The count of 23,943,826 refers to
the released aligned records, not automatically to newly acquired specimens. We
will separate (i) source measurements from public studies, (ii) any newly acquired
in-house measurements, and (iii) newly created harmonized/derived artifacts. We will
not equate aggregation with new biological acquisition.

\needinfo{Insert a source-audited comparison table giving, for sMMC-22M overall and
for the genuinely in-house subset, the numbers of studies, samples, patients/animals,
organs, platforms, spots/bins/cells, and unique cells not present in HEST-1K or
STimage-1K4M. Include source IDs and deduplication rules.}

\medskip
\textbf{7Gar-4.}\quad
\revcomment{The spot-to-cell component uses existing bin2cell-style methodology and
is not positioned against prior work.}

\response
We agree and will not present bin-to-cell aggregation as a new decomposition
algorithm. The dataset contribution is the provenance-preserving harmonization,
cell-centered multimodal interface, leakage-controlled split definitions, and
benchmarking across organs/platforms/context. The revision will explain the
spot/bin-to-cell construction before downstream experiments and expand related work
on Bin2Cell and other spot-to-cell or super-resolution methods. We will state that
derived Visium HD targets inherit the assumptions of those methods.

\medskip
\textbf{7Gar-5.}\quad
\revcomment{STBoost, STBoost-Ref, ``Ours,'' STBoosted BLEEP, BLEEP, Table 2, and the
inference protocol are unclear.}

\response
We will use one consistent terminology:

\begin{itemize}
  \item \textbf{STBoost} is the data-interface framework that converts a compatible
  spot-level pipeline to cell-aligned training and evaluation records.
  \item \textbf{BLEEP} is the published image-to-expression baseline.
  \item \textbf{STBoosted BLEEP} is BLEEP retrained and evaluated through the
  cell-aligned STBoost interface.
  \item \textbf{STBoost-Ref} is our native retrieval-based reference predictor;
  ``Ours'' in Figure 4 refers to STBoost-Ref and will be renamed accordingly.
\end{itemize}

At query time, STBoost-Ref receives only the local and wider-context histology crops
and outputs a cell-aligned expression vector. Query expression is never an input.
Expression is used only to build training-split reference entries. Table 2 will be
retitled to define a ``cell unit'' as one aligned cell record and will point forward
to the construction and split sections. We will introduce BLEEP and STBoost before
their first use, define AK/AD/AL in the text, add the missing task/metric/ratio
definitions to Figure 2, and remove repetitive framing.

\medskip
\textbf{7Gar-6.}\quad
\revcomment{Data accessibility, reproducibility, and reference formatting are
inadequate.}

\response
We agree. The revision will contain a versioned release manifest that distinguishes
directly measured, processed, generated, and model-output fields; split files;
checksums; licenses; preprocessing commands; and a minimal example record.

\needinfo{Insert a verified anonymous URL that reviewers can open, the exact assets
available there at rebuttal time, the release version/checksum, and the timetable for
any remaining restricted assets.}

We will also regenerate the bibliography using the required NeurIPS style so that
author lists are not uniformly truncated to ``et al.'' and will verify every
appendix link before submission.

\end{document}
