\documentclass[10pt]{article}
\usepackage[margin=0.72in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{array}
\usepackage[hidelinks]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.42em}
\setlength{\emergencystretch}{2em}

\newcommand{\revcomment}[1]{\textcolor{black}{\textbf{Reviewer comment. #1}}}
\newcommand{\questionsep}{\par\vspace{1.25em}}
\newcommand{\response}{\textbf{Response.}\enspace}
\newcommand{\needexp}[1]{\textcolor{red}{\textbf{[EXPERIMENT TO INSERT:} #1\textbf{]}}}
\newcommand{\needinfo}[1]{\textcolor{red}{\textbf{[AUTHOR INPUT TO INSERT:} #1\textbf{]}}}

\begin{document}

\begin{center}
{\Large Response to Reviewer vCPF}\\[2pt]
Submission 13175
\end{center}

\textcolor{red}{Red text marks experimental results or author-supplied facts that must be
inserted and checked before submission.}

\textbf{Opening response.}
We thank the reviewer for the careful and constructive assessment. We agree with the
three central requests: quantify uncertainty in the Visium HD cell construction,
demonstrate breadth beyond a few case studies, and calibrate low correlations with
biologically interpretable and simple baselines. We also agree that in-domain and
sample-held-out results answer different questions and should not be conflated.

\questionsep
\textbf{vCPF-1.}\quad
\revcomment{How reliable is Visium HD bin-to-cell aggregation? How are boundary bins
assigned, and do segmentation errors affect the resulting profiles?}

\response
We will clarify the claim boundary first. Xenium supplies natively cell-resolved
transcript locations and platform-defined cell masks. Visium HD instead supplies
dense native 2-\(\mu\)m bins; we register these bins to the H\&E image, segment cell
footprints, and aggregate bin counts to the aligned footprints. Thus, Visium HD
records are \emph{cell-aligned computational targets}, not direct single-cell
measurements. We will replace wording that could imply otherwise.

The audited released rule assigns a bin when its closed 2-\(\mu\)m square intersects
a CellViT polygon. If multiple polygons claim a bin, the bin is assigned to the
nearest CellViT centroid in full-resolution image coordinates; exact-distance ties
use the lower raw-cell index. The 8-\(\mu\)m files are legacy QC/fallback artifacts,
not the canonical expression targets.

\needinfo{Confirm the CellViT model/version, registration implementation, and all
released-pipeline QC thresholds.}

All nine perturbation aggregations are complete for lung A, lung B, and ovary.
Relative to the released rule, strict-interior assignment retained
\(62.5\%/56.1\%/80.7\%\) of cells and
\(16.0\%/11.0\%/20.5\%\) of assigned bins; one-bin erosion retained
\(46.0\%/37.9\%/72.0\%\) of cells and \(18.9\%/12.2\%/26.0\%\) of bins.
One-bin dilation retained \(100.0\%--100.1\%\) of cells but increased assigned bins
to \(181.9\%--196.2\%\) of default. Thus, the construction is materially sensitive
to the boundary rule and should not be treated as direct single-cell ground truth.

\needexp{On identical common cells and genes, insert expression Pearson/Spearman,
HVG/marker-rank stability, coarse-state concordance, and fixed-checkpoint
image-to-gene sensitivity with confidence intervals.}

These results will be reported separately for Visium HD and Xenium, because
combining them would obscure the uncertainty specific to computational aggregation.

\questionsep
\textbf{vCPF-2.}\quad
\revcomment{The main experiments cover only a few cases. Please provide a compact
summary across more organs or platforms.}

\response
We have a directly comparable five-organ Visium HD analysis using the same
in-domain top-50-gene protocol. The corrected results below compare STBoost-Ref with
BLEEP; all values are computed on each organ separately.

\begin{center}
\begin{tabular}{lrrrr}
\toprule
& \multicolumn{2}{c}{STBoost-Ref} & \multicolumn{2}{c}{BLEEP} \\
\cmidrule(lr){2-3}\cmidrule(lr){4-5}
Organ & Gene \(r\) & Cell \(r\) & Gene \(r\) & Cell \(r\) \\
\midrule
Ovary  & 0.4523 & 0.8379 & 0.4239 & 0.8212 \\
Lung   & 0.5178 & 0.6042 & 0.4241 & 0.5622 \\
Breast & 0.3366 & 0.2345 & 0.0079 & 0.1282 \\
Kidney & 0.3643 & 0.5112 & 0.3356 & 0.5369 \\
Tonsil & 0.3817 & 0.8193 & 0.1809 & 0.7808 \\
\bottomrule
\end{tabular}
\end{center}

This table supports breadth across five tissues but also exposes substantial
heterogeneity; it does not justify claiming that all 25 organs are equally
validated. We will state that boundary explicitly and provide the gene-selection,
split, and sample-size details next to the table.

\needexp{Add the planned lightweight benchmark over the final set of organs and both
platforms, with per-organ/per-platform values, organ-macro averages, sample and cell
counts, gene-panel overlap, and uncertainty. Keep Xenium and Visium HD summaries
separate.}

\questionsep
\textbf{vCPF-3.}\quad
\revcomment{How should low gene-wise correlations, especially under transfer, be
interpreted biologically? Please add marker/cell-type-gene or spatial-only/metadata-only
baselines.}

\response
We agree that the low full-gene correlations are important negative results, not
numbers to hide. Full-gene evaluation contains many sparse and weakly predictable
genes; cross-sample shifts further change morphology, tissue composition, and
acquisition conditions. For the lung experiment, STBoost-Ref obtains gene-wise
Pearson/Spearman and cell-wise Pearson correlations of
\(0.0259/0.0268/0.4112\) in-domain and
\(0.0124/0.0137/0.2820\) sample-held-out over the full panel. These values indicate
that histology alone is not a reliable replacement for measured expression.

As an explicitly post-hoc upper-bound diagnostic, the corresponding selected
50-gene results are \(0.5117/0.5069/0.5979\) in-domain and
\(0.2986/0.2405/0.3451\) sample-held-out (gene Pearson/Spearman/cell Pearson).
Separately, marker-derived states from 111,772 lung cells reach \(0.5922\)
balanced accuracy (ARI \(0.1362\)); both results caution against cell-by-cell
interpretation.

On \emph{native Xenium targets}, four existing 70/10/20 random-cell-split
evaluations (training-only gene selection) gave:

\begin{center}
\small
\begin{tabular}{lrrrrr}
\toprule
Organ & Cells & Genes & Gene \(r/\rho\) & Coord. \(r\) & Cell \(r/\rho\) \\
\midrule
Colon  & 77,636  & 10 & 0.541/0.544 & 0.238 & 0.666/0.637 \\
Breast & 114,907 & 10 & 0.512/0.585 & 0.116 & 0.546/0.519 \\
Ovary  & 4,000   & 10 & 0.406/0.459 & 0.285 & 0.644/0.543 \\
Skin   & 13,696  & 10 & 0.509/0.384 & 0.257 & 0.508/0.443 \\
\bottomrule
\end{tabular}
\end{center}

Recovered markers include TFF3/EPCAM, IGKC/JCHAIN, MUC1/GATA3, and
DES/MYH11/MYLK; ovary excludes three deprecated controls. These quantify
within-sample interpolation, not sample-held-out transfer. In 100 spatial-block
bootstrap replicates, image gene-\(r\) 95\% CIs were
\([0.518,0.558]\), \([0.487,0.530]\), \([0.377,0.424]\), and
\([0.467,0.525]\); none overlapped the coordinate-only CIs.

\needexp{Complete fixed-panel, sample-held-out native-Xenium evaluation with
marker, program, and coarse-state metrics; Average, Worst, and Gap; and a metadata baseline.}

\questionsep
\textbf{vCPF-4.}\quad
\revcomment{In-domain splits may measure local interpolation and spatial
autocorrelation rather than robust generalization.}

\response
We agree. We will relabel the in-domain setting as an interpolation diagnostic and
use sample-held-out/cross-study transfer for the main generalization claim. In the lung
experiment, the drop from \(0.4112\) to \(0.2820\) in full-panel cell-wise Pearson
correlation illustrates this gap.

\needexp{Add a distance-buffered in-domain split and a coordinate-only/spatial-neighbor
baseline, reporting performance as a function of the minimum train--test distance.}

\questionsep
\textbf{vCPF-5.}\quad
\revcomment{The ovarian age-shift experiment is narrow and does not establish that
all context variables can be evaluated systematically.}

\response
We agree and will describe it as one case study, not as proof of systematic context
evaluation. Moreover, the current comparisons differ in patient/tumour context and
gene-panel size, so they cannot identify a pure age effect. We will define AK, AD,
and AL as anonymized ovarian sample identifiers and state their ages and other known
covariates explicitly.

\needexp{Rerun the ovarian comparison on the identical shared gene panel and matched
preprocessing, report sample/cell counts and uncertainty, and rewrite the conclusion
as an age-associated shift only if the result remains supported after acknowledging
patient and tissue-state confounding.}

\questionsep
\textbf{vCPF-6.}\quad
\revcomment{Users need to know which released fields are direct measurements and
which are generated or processed.}

\response
We will add a field-level provenance manifest:

\begin{center}
\begin{tabular}{p{0.18\linewidth}p{0.73\linewidth}}
\toprule
Provenance & Examples \\
\midrule
Directly measured &
H\&E image; Xenium transcript coordinates and platform cell masks; Visium HD
2-\(\mu\)m bin counts; source-study metadata as originally reported. \\
Processed &
Registered coordinates; segmented footprints; Visium HD bin-to-cell aggregated
matrices; local/context crops; normalized matrices; split indices; communication
summaries computed from molecular profiles. \\
Generated &
Metadata-grounded textual captions and model predictions. Generated text is an
auxiliary field and is not molecular ground truth. \\
\bottomrule
\end{tabular}
\end{center}

\needinfo{Insert the verified anonymous data/code URL, release version, licenses, and
an exact list of which raw, processed, generated, and split files are publicly
available at rebuttal time.}

\needexp{Insert factuality evaluation of generated captions: sampling design,
number/expertise of human raters, rubric, error categories, agreement, and supported
versus unsupported statement rates. Until validated, describe captions as optional
machine-generated annotations.}

\end{document}
